Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-22 article/ms.tex
Expanded abstract, slightly modified some of the place holder pics

Stellar absorption spectra act as a record of the primordial conditions within which the star formed. Stars displaying unusual elemental abundances provide are of particular interest; these rare stars often offer clues about astrophysical events and objects that may no longer exist in our galaxy. Stars with  depleted Mg and enhanced K abundances, measured as [Mg/Fe] and [K/Fe], have thus far only been found in the two massive globular clustersr NGC 2419 and NGC 2808. The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. A satisfactory explanation for this signature has potential to influence theories of globular cluster formation and shed light on the long-standing problem of the underestimation of stars with typical galactic values of [K/Fe]. The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this survey. Here we present 113 candidate field stars (from a sample size of \LamostGiants \ giants from \lamost \ DR2) that have spectra consistent with anomalously depleted [Mg/Fe] and enhanced [K/Fe] abundances, though none with abundances comparable to the extreme population of stars identified in NGC 2419.

%454180 RGB stars from the low resolution LAMOST DR2 survey were searched for anomalously high K and depleted Mg signatures. This study represents the largest search for field stars containing the Mg-K anti-correlation so far identified only in the globular NGC 2419 and NGC 2808. 23 stars displaying absorption spectra with over-abundant K and depleted Mg accross a range of metalicities were identified, but none were identified as having [Mg/Fe] or [K/Fe] consistent with the Mg depleted population found in NGC 2419. The abundances in these 23 stars are estimated at ranging between [INSERT RANGE FOR K AND MG HERE BASED OFF LAMOST DATA]. High resolution spectra for three stars (1 of which is not included among the final count of 23 spectral candidates for the signiature for reasons relating to the LAMOST signal quality for that star, despite having the highest K abundance of the three at [K/Fe]=1.54) selected based on observability characteristics were obtained using the Las Campanas Observatory, and for these stars elemental abundances for heavy elements such as Sc and V are also presented.
\end{abstract}

>>>>

Stellar absorption spectra act as a record of the primordial conditions within which the stars formed. Stars displaying unusual elemental abundances are of particular interest; these rare stars often offer clues about astrophysical events and objects that may no longer exist in our galaxy. Stars with  depleted Mg and enhanced K abundances, measured as [Mg/Fe] and [K/Fe], have thus far only been found in the two massive globular clusters NGC 2419 and NGC 2808. The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. A satisfactory explanation for this signature has potential to influence theories of globular cluster formation and shed light on the long-standing problem of the underestimation of [K/Fe] among even 'normal' field stars in the Milky Way. The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this paper. Here we present 113 candidate field stars (from a sample size of \LamostGiants \ giants from \lamost \ DR2) that have spectra consistent with slightly depleted [Mg/Fe] and significantly enhanced [K/Fe] abundances. None of these stars have abundances comparable to the extreme population of stars identified in NGC 2419. These stars are of a range of metalicities, and a new anti-correlation between [K/Fe] and [Fe/H] can be observed within the sample, although the veracity of said relation remains questionable. Two distinct populations can be formed by Na abundance within the sample, with 30\% of the candidates having calculated abundances well above typical galactic levels. Two scenarios designed at explaining the data are put forth, and the implications for select existing polluter candidate proposals are briefly discussed. These candidate stars should provide guidance for follow up surveys and modelling attempts attempting to determine the origin of the Mg-K anti-correlation.

\end{abstract}
